Quantifying Directionality and Innovation Output in Sweden's Transition to a Forest-Based Bioeconomy

### 2024-09-12 paper.qmd
refactor to pixi

from src.figures import *
from src.utils import get_project_root, format_table
from src.data_handling import database

>>>>

from swinno_bioeconomy_directionality.figures import *
from swinno_bioeconomy_directionality.utils import get_project_root, format_table
from swinno_bioeconomy_directionality.data_handling import database
